MS-4.2 Types of Relationships

### 2021-01-19 ms-a4-2_non-linear-relationships.rmd
Update style.css to match latex templates, added ms-a1, removed additional pages from html

# Exponential Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Exponential Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Quadratic Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Quadratic Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_d_quadratic-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

# Reciprocal Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_e_reciprocal-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

# Reciprocal Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_f_reciprocal-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

# Inverse Variation [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_g_inverse-variation.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

# Miscellaneous Problems [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_h_miscellaneous-problems.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

>>>>

# Exponential Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Exponential Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@

# Quadratic Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}

@@
